### 2019-02-27 sections/language.tex
add text about typing rules and use beta for references

Typing rules are of the form $\RelationT$, which should be read as \enquote{in environment $\Gamma$ and store typing $\Sigma$, expression $e$ has type $\tau$}.
Typing rules for expressions in the host language are presented in the appendix.
The typing rules for pretasks are given in \cref{fig:typing-rules}.
\todo{Say someting about why we need beta, and use beta in the acutal typing rule}
\todo{Alejandro: Is there anything surprising? Say what}

>>>>

Typing rules are of the form $\RelationT$, which should be read as \enquote{in environment $\Gamma$ and store typing $\Sigma$, expression $e$ has type $\tau$}.
Typing rules for expressions in the host language are presented in the appendix.
The typing rules for pretasks are given in \cref{fig:typing-rules}.
Most typing rules lift the type of their subexpressions into the $\Task$-type.
The typing rules for steps make sure the continuations $e_2$ are functions which accept a well-typed value from the left hand side (\refrule{T-Then}, \refrule{T-Next}).
References, and therefore shared editors, can only be of a basic type so they do not introduce implicit recursion (\refrule{T-Update}).
